---
title: "Wrangle"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
library(shinyjs)
library(knitr)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
gradethis::gradethis_setup()
```

## Welcome

Data wrangling includes data transformation, filtering, reshaping, and cleaning. There is currently no tool that teaches data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. Tools like this exist for algorithms and software engineering (HackerRank, LeetCode), but not specifically for data wrangling

```{r echo = FALSE, results='asis', include=FALSE}
make_topic <- function(topic_name, question_fun, solution_fun, params) { 
  browser()
  src <- map(list(question_fun, solution_fun),
             ~pmap(params, .x))
  src[[1]] <- append(list(paste0("## ", topic_name)), src[[1]])
  src
}

make_regression_question <- function(in_var) {
  knit_expand(text=c("### Regress `mpg` on `{{in_var}}`",
                     '```{r lm-{{in_var}}, exercise = TRUE}',
                     '#Enter your code here',
                     '```'))
}

make_regression_solution <- function(in_var) {
  knit_expand(text=c('```{r lm-{{in_var}}-solution}',
                     'lm(mpg ~ {{in_var}}, data=mtcars)',
                     '```',
                     '```{r lm-{{in_var}}-check}',
                     'solution <- lm(mpg ~ {{in_var}}, data=mtcars)
                     test <- 2',
                     'grade_this({
  if (length(waldo::compare(.result, solution, ignore_formula_env = T)) == 0) {
    pass("Great work!")
  }
  fail("Try again!")
})',
'```'))
}

regression_params <- tibble(in_var = names(mtcars)[-1])

src <- make_topic("Regression", make_regression_question,
                  make_regression_solution, regression_params)

res <- knit_child(text = unlist(src))
```

`r res`

```{r, echo=FALSE}
# js_code <- "shinyjs.update_location = function(exercise){var base_url = window.location.href.replace(window.location.hash,''); var href = base_url + '#section-' + exercise; window.location = href;}"
# 
# #make select input jump to new page
# useShinyjs(rmd = TRUE)
# extendShinyjs(text = js_code, functions = c("update_location"))
```

```{r, context="server"}
# observeEvent(input$ex_topic, {
#   js$update_location(input$ex_topic)
# })
```