---
title: "Wrangle"
output: 
  learnr::tutorial:
    progressive: false
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
library(shinyjs)
library(knitr)
library(Lahman)
library(AER)
data("DoctorVisits")
chick_weight <- ChickWeight <- as_tibble(ChickWeight)
orange <- Orange <- as_tibble(Orange)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
gradethis::gradethis_setup()

db_con <- DBI::dbConnect(RSQLite::SQLite(), dbname = ":memory:")
DBI::dbWriteTable(db_con, "iris", iris %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "mtcars", mtcars %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "chick_weight", ChickWeight %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "diamonds", ggplot2::diamonds %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "Orange", Orange %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "PlantGrowth", PlantGrowth %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "airquality", airquality %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "ToothGrowth", ToothGrowth %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "Batting", Lahman::Batting %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "Salaries", Lahman::Salaries %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))
DBI::dbWriteTable(db_con, "storms", dplyr::storms %>% 
                    rename_all(~tolower(gsub("\\.", "_", .x))))

```

## Welcome to **Wrangle**

Data wrangling includes data transformation, filtering, reshaping, and cleaning. We made **Wrangle** to teach data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. **Wrangle** has problems for R and SQL.

We hope **Wrangle** helps you on your data science journey!

**Wrangle** is still a work in progress — if you have any feedback [please submit it here](https://docs.google.com/forms/d/e/1FAIpQLSfg0RSzLw2MXCAUJMgsXCGeey7zA5y_pjVt8P24eeQySNOgaA/viewform?usp=sf_link).

Here are some additional resources to help you learn data wrangling through R:

* [R for Data Science](https://r4ds.had.co.nz/index.html)
* [RStudio Education](https://education.rstudio.com/learn/beginner/)
* [Codeacademy](https://www.codecademy.com/learn/learn-r)

...and SQL:

* [Mode SQL Tutorial](https://mode.com/sql-tutorial/)
* [W3 Schools](https://www.w3schools.com/sql/)
* [Codeacademy](https://www.codecademy.com/learn/learn-sql)
* [KhanAcademy](https://www.khanacademy.org/computing/computer-programming/sql)
* [SQL Zoo](https://sqlzoo.net/wiki/SQL_Tutorial)

Created by [Akshay Swaminathan](https://www.linkedin.com/in/akshay-swaminathan-68286b51/) and [Lathan Liou](https://lathanliou.com/)

```{r echo = FALSE, results='asis', include=FALSE}
make_topic <- function(topic_name, question_fun, solution_fun, params) { 
  src <- map(list(question_fun, solution_fun),
             ~pmap(params, .x))
  src[[1]] <- append(list(paste0("## ", topic_name)), src[[1]])
  src
}

make_question <- function(exercise_title,
                          exercise_text,
                          exercise_name,
                          sql = F,
                          ...) {
  
  if (sql) {
    text_ <- c("### {{exercise_title}}",
                     "{{exercise_text}}",
                     '```{sql {{exercise_name}}, exercise = TRUE, connection = "db_con"}',
                     '--Enter your code here',
                     '```')
  } else {
    text_ <- c("### {{exercise_title}}",
                     "{{exercise_text}}",
                     '```{r {{exercise_name}}, exercise = TRUE}',
                     '#Enter your code here',
                     '```')
  }
  
  knit_expand(text = text_)
}


make_solution <- function(exercise_name,
                          check_code = 0,
                          solution_code,
                          sql = F,
                          ...) {
  
  result_string <- ifelse(sql, 
                          "solution_return <- function() {DBI::dbGetQuery(db_con, '{{solution_code}}')}", 
                          "solution_return <- function() { {{solution_code}} }")
  
  if (check_code == 1) {
    check_chunk <- c('```{r {{exercise_name}}-code-check}',
                     'grade_code()')
  } else {
    check_chunk <- c('```{r {{exercise_name}}-check}',
                     "set.seed(50)",
                     result_string,
                     #'solution <- {{solution_code}}',
                     'solution <- solution_return()',
                     'grade_this({
  if (length(waldo::compare(.result, solution, ignore_formula_env = T)) == 0) {
    pass("Great work!")
  }
  fail("Try again!")
  # fail(waldo::compare(.result, solution, ignore_formula_env = T))
})')
  }
  
  if (sql) {
    result_string <- "DBI::dbGetQuery(db_con, .solution_code)"
    knit_expand(text=c('```{sql {{exercise_name}}-solution, connection = "db_con"}',
                     '{{solution_code}}',
                     '```',
                     check_chunk,
                     '```'))
  } else {
    knit_expand(text=c('```{r {{exercise_name}}-solution}',
                     '{{solution_code}}',
                     '```',
                     check_chunk,
                     '```'))
  }
  
  
}

googlesheets4::gs4_deauth()
param_google_sheets <- "https://docs.google.com/spreadsheets/d/18IBUDzUPxJg69Z9J9io0-9Hn39DXfzmhjWjDCW9ghDk/edit#gid=0"
all_sheets_base <- googlesheets4::sheet_names(param_google_sheets) 
all_sheets <- all_sheets_base[which(!grepl("\\[exclude\\]", all_sheets_base))]
all_params <- map(all_sheets, ~googlesheets4::read_sheet(param_google_sheets, sheet = .x)) %>% 
  setNames(all_sheets)

all_params$`Queries: SQL` <- all_params %>% 
  map_dfr(function(param_df) {
    if ("sql_code" %in% names(param_df)) {
      param_df %>% 
        select(-solution_code) %>% 
        rename(solution_code = sql_code)
    } else {
      return(NULL)
    }
  }) %>% 
  filter(!is.na(solution_code)) %>% 
  mutate(exercise_title = paste0("Exercise ", row_number()),
         exercise_name = paste0("sql", row_number())) %>% 
  mutate(sql = T)

all_params <- all_params[rev(sort(names(all_params)))]

all_src <- imap(all_params, ~make_topic(.y, make_question, make_solution, .x))
all_res <- map(all_src, ~knit_child(text = unlist(.x)))

```

```{r echo = FALSE, results='asis', message = F}
map(all_res, cat)
```


