---
title: "Wrangle: `purrr`"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
library(shinyjs)
library(knitr)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
gradethis::gradethis_setup()
```

## Welcome

Data wrangling includes data transformation, filtering, reshaping, and cleaning. There is currently no tool that teaches data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. Tools like this exist for algorithms and software engineering (HackerRank, LeetCode), but not specifically for data wrangling

```{r echo = FALSE, results='asis', include=FALSE}
make_topic <- function(topic_name, question_fun, solution_fun, params) { 
  src <- map(list(question_fun, solution_fun),
             ~pmap(params, .x))
  src[[1]] <- append(list(paste0("## ", topic_name)), src[[1]])
  src
}

make_question <- function(exercise_title,
                          exercise_text,
                          exercise_name,
                          ...) {
  knit_expand(text=c("### {{exercise_title}}",
                     "{{exercise_text}}",
                     '```{r {{exercise_name}}, exercise = TRUE}',
                     '#Enter your code here',
                     '```'))
}

make_solution <- function(exercise_name,
                          check_code = 0,
                          solution_code,
                          ...) {
  if (check_code == 1) {
    check_chunk <- c('```{r {{exercise_name}}-code-check}',
                     'grade_code()')
  } else {
    check_chunk <- c('```{r {{exercise_name}}-check}',
                     "set.seed(50)",
                     'solution <- {{solution_code}}',
                     'grade_this({
  if (length(waldo::compare(.result, solution, ignore_formula_env = T)) == 0) {
    pass("Great work!")
  }
  fail("Try again!")
})')
  }
  knit_expand(text=c('```{r {{exercise_name}}-solution}',
                     '{{solution_code}}',
                     '```',
                     check_chunk,
                     '```'))
}

googlesheets4::gs4_deauth()
param_google_sheets <- "https://docs.google.com/spreadsheets/d/18IBUDzUPxJg69Z9J9io0-9Hn39DXfzmhjWjDCW9ghDk/edit#gid=0"

map_params <- googlesheets4::read_sheet(param_google_sheets)
map2_params <- googlesheets4::read_sheet(param_google_sheets, sheet = "Sheet2")

src <- make_topic("map", make_question,
                  make_solution, map_params)
src2 <- make_topic("map2", make_question,
                  make_solution, map2_params)

res <- knit_child(text = unlist(src))
res2 <- knit_child(text = unlist(src2))
```

`r res`

`r res2`
