---
title: "Wrangle"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
library(knitr)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
```

## Welcome

Data wrangling includes data transformation, filtering, reshaping, and cleaning. There is currently no tool that teaches data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. Tools like this exist for algorithms and software engineering (HackerRank, LeetCode), but not specifically for data wrangling

## Exercises

Please select a following question based on: (PLACEHOLDER)

```{r, echo=FALSE}
selectizeInput("ex_topic", "Topic", choices = list(
  Select = c("Choose one" = ""),
  Indexing = c(`Exercise 1` = "ex1", `Exercise 2` = "ex2"),
  Subsetting = c(`Exercise 3` = "ex3", `Exercise 4` = "ex4")
  )
)
```

or

```{r, echo=FALSE}
selectizeInput("ex_level", "Difficulty", choices = list(
  Select = c("Choose one" = ""),
  Easy = c(`Exercise 1` = "ex1", `Exercise 3` = "ex3"),
  Intermediate = c(`Exercise 2` = "ex2", `Exercise 4` = "ex4")
  )
)
```

```{r echo = FALSE, results='asis', include=FALSE}
make_question <- function(in_var) {
    knit_expand(text=c("### Regress `mpg` on `{{in_var}}`", 
                     '```{r lm-{{in_var}}, exercise = TRUE}', 
                     '#Enter your code here', 
                     '```'))
}

make_solution <- function(in_var) {
  knit_expand(text=c('```{r lm-{{in_var}}-solution}', 
                     'lm(mpg ~ {{in_var}}, data=mtcars)', 
                     '```'))
}

# Generate question and solution chunks
src <- map(list(make_question, make_solution), 
           ~map(names(mtcars)[-1], function(variable) .x(variable)))

res <- knit_child(text = unlist(src))
```

`r res`
