---
title: "Wrangle"
output: 
  learnr::tutorial:
    progressive: false
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
library(shinyjs)
library(knitr)
library(Lahman)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
gradethis::gradethis_setup()
```

## Welcome

Data wrangling includes data transformation, filtering, reshaping, and cleaning. There is currently no tool that teaches data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. Tools like this exist for algorithms and software engineering (HackerRank, LeetCode), but not specifically for data wrangling.

We hope Wrangle helps you on your data science journey!

Note: Wrangle is still a work in progress — if you have any feedback [please submit it here](https://docs.google.com/forms/d/e/1FAIpQLSfg0RSzLw2MXCAUJMgsXCGeey7zA5y_pjVt8P24eeQySNOgaA/viewform?usp=sf_link).

```{r echo = FALSE, results='asis', include=FALSE}
make_topic <- function(topic_name, question_fun, solution_fun, params) { 
  src <- map(list(question_fun, solution_fun),
             ~pmap(params, .x))
  src[[1]] <- append(list(paste0("## ", topic_name)), src[[1]])
  src
}

make_question <- function(exercise_title,
                          exercise_text,
                          exercise_name,
                          ...) {
  knit_expand(text=c("### {{exercise_title}}",
                     "{{exercise_text}}",
                     '```{r {{exercise_name}}, exercise = TRUE}',
                     '#Enter your code here',
                     '```'))
}

make_solution <- function(exercise_name,
                          check_code = 0,
                          solution_code,
                          ...) {
  if (check_code == 1) {
    check_chunk <- c('```{r {{exercise_name}}-code-check}',
                     'grade_code()')
  } else {
    check_chunk <- c('```{r {{exercise_name}}-check}',
                     "set.seed(50)",
                     "solution_return <- function() { {{solution_code}} }",
                     #'solution <- {{solution_code}}',
                     'solution <- solution_return()',
                     'grade_this({
  if (length(waldo::compare(.result, solution, ignore_formula_env = T)) == 0) {
    pass("Great work!")
  }
  fail("Try again!")
  # fail(waldo::compare(.result, solution, ignore_formula_env = T))
})')
  }
  knit_expand(text=c('```{r {{exercise_name}}-solution}',
                     '{{solution_code}}',
                     '```',
                     check_chunk,
                     '```'))
}

googlesheets4::gs4_deauth()
param_google_sheets <- "https://docs.google.com/spreadsheets/d/18IBUDzUPxJg69Z9J9io0-9Hn39DXfzmhjWjDCW9ghDk/edit#gid=0"
all_sheets_base <- googlesheets4::sheet_names(param_google_sheets) 
all_sheets <- all_sheets_base[which(!grepl("\\[exclude\\]", all_sheets_base))]
all_params <- map(all_sheets, ~googlesheets4::read_sheet(param_google_sheets, sheet = .x)) %>% 
  setNames(all_sheets)

all_src <- imap(all_params, ~make_topic(.y, make_question, make_solution, .x))
all_res <- map(all_src, ~knit_child(text = unlist(.x)))

```

```{r echo = FALSE, results='asis', message = F}
map(all_res, cat)
```

## About
Created by Akshay Swaminathan and Lathan Liou
