---
title: "Wrangle"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  An interactive tool to teach data wrangling in R.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(shiny)
tutorial_options(exercise.timelimit = 60)
knitr::opts_chunk$set(error = TRUE)
```

## Welcome

Data wrangling includes data transformation, filtering, reshaping, and cleaning. There is currently no tool that teaches data wrangling through interactive exercises that improve skills through high volume repetition/problem solving. Tools like this exist for algorithms and software engineering (HackerRank, LeetCode), but not specifically for data wrangling

## Exercises

Please select a following question based on: (PLACEHOLDER)

```{r, echo=FALSE}
selectizeInput("ex_topic", "Topic", choices = list(
  Select = c("Choose one" = ""),
  Indexing = c(`Exercise 1` = "ex1", `Exercise 2` = "ex2"),
  Subsetting = c(`Exercise 3` = "ex3", `Exercise 4` = "ex4")
  )
)
```

or

```{r, echo=FALSE}
selectizeInput("ex_level", "Difficulty", choices = list(
  Select = c("Choose one" = ""),
  Easy = c(`Exercise 1` = "ex1", `Exercise 3` = "ex3"),
  Intermediate = c(`Exercise 2` = "ex2", `Exercise 4` = "ex4")
  )
)
```

<!-- To write an exercise -->
<!-- ```{r name, exercise = TRUE} -->
<!-- ``` -->
<!-- ```{r name-solution} -->
<!-- #insert code solution -->
<!-- ``` -->
<!-- -->
<!-- <div id="name-hint"> -->
<!-- **Hint:** -->
<!-- </div> -->
